Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-28 sports_analytics.Rmd
NFL expected points section updates.

@@

@urschel2011 Examines decsions on kick offs (surprise on sides or regular kick off AND accept touchback or return kick) using an expected points frame work.  Shows that teams are moderately risk and loss averse.
https://www.eng.buffalo.edu/~jzhuang/Papers/JQAS_NFL_2011.pdf

>>>>

@urschel2011 uses expected points to evaluate NFL coaching decisions on kickoffs.  Specifically, they look at surprise on-sides kicks vs regular kickoff and the decision to accept a touchback vs returning kickoff.  Using data from the 2009 NFL season, the conclude, as many have, that coaches in the NFL tend to make conservative decisions.

<!-- decsions on kick offs (surprise on sides or regular kick off AND accept touchback or return kick) using an expected points frame work.  Shows that teams are moderately risk and loss averse. -->
<!-- https://www.eng.buffalo.edu/~jzhuang/Papers/JQAS_NFL_2011.pdf -->

@@

<!-- @urschel2011 Examines decsions on kick offs (surprise on sides or regular kick off AND accept touchback or return kick) using an expected points frame work.  Shows that teams are moderately risk and loss averse. -->
<!-- https://www.eng.buffalo.edu/~jzhuang/Papers/JQAS_NFL_2011.pdf -->
